IGRINS spectra of \name

### 2016-05-04 document/ms.tex
Add a table showing the 4 approaches with full spectrum vs order-by-order, and one or two components.  Issue #19

\subsection{Model design and implementation considerations}

\subsubsection{Approach 11: Whole spectrum with a single photospheric component (Czekala et al. 2015)}

@@

\subsubsection{Approach 12: Deriving unique Teff in each order}

@@

\subsubsection{Approach 21: Whole spectrum with two components}

@@

\subsubsection{Approach 22: Order-by-order with two components}

>>>>

\begin{tabular}{ r| p{5cm} | p{5cm} | }
\multicolumn{1}{r}{}
 &  \multicolumn{1}{c}{Whole spectrum (Gibbs Sampling)}
 & \multicolumn{1}{c}{Order-by-order (emcee)} \\
\cline{2-3}
Single component photosphere & \citet{2015ApJ...812..128C}: Poor model for spotted stars & Sec. \ref{sec:approach12}- plausible evidence for starspots if $\teff$ varies with order \\
\cline{2-3}
Two component photosphere & \ref{sec:approach21}- Statistically principled inference on starspot properties given the whole spectrum.  But strongly correlated dimensions impose challenge on MCMC tuning. & \ref{sec:approach22}- Multiple independent posteriors of starspot properties.  But combining inferences is heuristic.  \\
\cline{2-3}
\end{tabular}

\subsection{Approach 11: Whole spectrum with a single photospheric component (Czekala et al. 2015)}

@@

\subsection{Approach 12: Deriving unique Teff in each order}
\label{sec:approach12}

@@

\subsection{Approach 21: Whole spectrum with two components}
\label{sec:approach21}

@@

\subsection{Approach 22: Order-by-order with two components}
\label{sec:approach22}
